DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/evaluation.tex
evaluation revision (WIP)

In evaluating the real-time efficacy of the DeepPicar, the methodology is consistent across all 
experiments. The performance of the platform is measured over a set of 1001 video frames that are 
each individually fed to the model. The processing time for the first frame is omitted as, due to 
cache warmup, it is uncharacteristically high and doesn't accurately represent the Picar's capabilities. 
A WCET of 50 ms, or 20 Hz, is used as a baseline to assess the platform's ability to complete all 
necessary real-time operations in a timely manner.

\subsection{Real-Time Operations}
We seek to determine if the DeepPicar is capable of consistently executing all necessary functions 
before their given deadlines. In the case of our platform, it has to process every given frame and get 
the predicted angles from the model within a WCET of 50 ms. In order to determine if this was achievable, 
we tested the platform by running a single model that utilized all 4 cpu cores and measured the time it 
took for each frame to be processed. The performance of the DeepPicar can be seen in Figure 6. We found 
that DeepPicar was able to completely process the vast majority of the provided frames within 50 ms, and 
was unable to do so for very few frames.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{ Real-time performance of the DeepPicar in processing 1000 frames.}
\end{figure}

>>>>

In this section, we experimentally analyze various real-time aspects
of the DeepPicar. This includes
(1) measurement based worst-case execution time (WCET) analysis of
deep learning inferencing,
(2) the effect of using multiple cores in accelerating inferencing,
(3) the effect of co-scheduling multiple deep neural network models,
and 
(4) the effect of co-scheduling memory bandwidth intensive co-runners.

\subsection{Setup}

The Raspberry Pi 3 Model B platform used in DeepPicar equip a Boardcom
BCM2837 SoC, which has a quad-core 64bit ARM Cortex-A53 cluster,
running at up to 1.2GHz. The chip also includes Broadcom's Videocore IV
GPU, although we did not use the GPU in our evaluation due to the lack
of sofware support (Tensorflow is not compatible with the GPU).
For software, we use Ubuntu MATE 16.04, Tensorflow 1.1 and python
2.7. We disabled DVFS (dynamic voltage frequency scaling) and
configure the clock speed of each core at the maximum 1.2GHz.

\subsection{Inference Timing for Real-Time Control}

For real-time control of a car (or any robots), the control loop
frequency must be sufficiently high so that the car can quickly
react to the changing environment and its internal states. In general,
control performance improves when the frequency is higher, though
computation time and the type of particular physical system are
factors in determining a proper control loop latency. While a standard
control system may be comprized of multiple control loops with
differning control frequencies---e.g., a inner control loop for lower-level
PD control, a outer loop for motion planning, etc.---DeepPicar's
control loop is a single layer, as shown earlier in
Figure~\ref{fig:controlloop}, as a single deep neural network
replaces the traditional multi-layer control pipline. (Recall
Figure~\ref{fig:end-to-end-control} on the differences between the
standard robotics control vs. end-to-end deep learning approach).
This means that the DNN interference operation must be completed
within the inner-most control loop update frequency. To understand
achievable control-loop update frequencies, we experimentally measured
the execution times of DeepPicar's DNN inference operations.

% 50-200Hz for quadcopters:
% https://robotics.stackexchange.com/questions/231/what-frequency-does-my-quadcopter-output-sense-calculate-output-update-loop-need

\begin{figure}[t]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

Figure~\ref{fig:control-loop-timing} shows the measured control loop
processing times of the DeepPicar in which 1001 image frames, from the
camera, are fed to the DNN, one frame per each control loop. The
measured time is total execution time of a control loop.

%% In evaluating the real-time efficacy of the DeepPicar, the methodology is consistent across all 
%% experiments. The performance of the platform is measured over a set of 1001 video frames that are 
%% each individually fed to the model. The processing time for the first frame is omitted as, due to 
%% cache warmup, it is uncharacteristically high and doesn't accurately represent the Picar's capabilities. 
%% A WCET of 50 ms, or 20 Hz, is used as a baseline to assess the platform's ability to complete all 
%% necessary real-time operations in a timely manner.

We seek to determine if the DeepPicar is capable of consistently executing all necessary functions 
before their given deadlines. In the case of our platform, it has to process every given frame and get 
the predicted angles from the model within a WCET of 50 ms. In order to determine if this was achievable, 
we tested the platform by running a single model that utilized all 4 cpu cores and measured the time it 
took for each frame to be processed. The performance of the DeepPicar can be seen in Figure 6. We found 
that DeepPicar was able to completely process the vast majority of the provided frames within 50 ms, and 
was unable to do so for very few frames.
